---
output:
  md_document:
    variant: markdown_github
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# About

This R data package contains data from IPUMS's Annual Social and Economic Supplement of the Current Population Survey (ASEC, i.e., CPS March Supplement), 1990-1999. All the currently avaiblable variables (as of Aug. 30, 2015) are included. 

See [IPUMS's codebooks](https://cps.ipums.org/cps/documentation.shtml) for documentations.

Research based on the IPUMS-CPS database should cite it as follows:

> Miriam King, Steven Ruggles, J. Trent Alexander, Sarah Flood, Katie Genadek, Matthew B. Schroeder, Brandon Trampe, and Rebecca Vick. Integrated Public Use Microdata Series, Current Population Survey: Version 3.0. [Machine-readable database]. Minneapolis: University of Minnesota, 2010.

# Installation

Install from github with 
```r
devtools::install_github("jjchern/cpsmar1990s")
```

Since there're 10 years of data, the package is kind of big (about 86 MB). It might take a while to download.

# Usage

```{r, message=FALSE, warning=FALSE}
library(cpsmar1990s)
library(dplyr)

# All the datasets
ls("package:cpsmar1990s", all = TRUE)

# All variables in cpsmar1993
names(cpsmar1993)

# Select a few variables
cpsmar1993 %>% 
  select(year, statefip, age, sex, race, educ99, fullpart) 

# Each variable is a "labelled" vector (from the `haven` package)
cpsmar1994$sex %>% str
attr(cpsmar1994$sex, "label") # like Stata's label
attr(cpsmar1994$sex, "labels") # like Stata's label values
```

